---
title: ""
output: 
  html_document:
    toc: FALSE
---

```{r, include = FALSE}
#just so I can use emoticons
#devtools::install_github("hadley/emo")
library(emo)
```

# Overview

This small website contains a collection of lists with links to various resources that are related to my ([Andreas Handel](https://www.andreashandel.com/)) research and teaching, as well as some general (academic) career content.

This mainly a collection of links to other sources. Some pages contain a few of my own thoughts on specific topics. The content is heavily biased toward my work. For research topics, the focus is in statistics/data analysis, infectious disease modeling and the R programming language. The other lists focus on research/academic careers and topics related to it.

Some lists contain a decent amount of information, others are fairly short/empty. All of the lists are subject to (infrequent) change/updates - whenever I get to it or come across sources I find interesting enough to 'bookmark' by adding them to one of the lists.

The main reason for these lists is so I can find stuff again. If others benefit from some of the listed links, even better.

If you have suggestions for updates/improvements or something doesn't work, let me know (using github issues or pull requests).  


# Content

## General Lists

The following lists contain mostly links and some of my own thoughts on specific topics.


- [Career Topics:](./Career_Resources.html) (Academic/research) career related resources. 

- [Communication Topics:](./Communication_Resources.html) How to communicate (scientific) information to various audiences.

- [Data Sources:](./Data_Resources.html) Where to find potentially interesting data.

- [Data Analysis and Stats:](./Dataanalysis_Resources.html) Data analysis and statistics related tasks, with a focus on R.

- [Infectious Disease Modeling:](./IDmodeling_Resources.html) Information that's useful for Infectious Disease modeling. 

- [Reading, managing and publishing papers:](./Literature_Resources.html) How to search and read the literature, how to stay up to date and manage references, how to publish.

- [R Coding Topics:](./R_Resources.html) Resources for learning R in general and with learning specific R topics.

- [Reproducible Research, Workflow management:](./ReproducibleResearch_Resources.html) Reproducible research (with a focus on the data analysis aspect) and links to tools (RMarkdown).


 
## Cheat Sheets

The following documents contain collections of R code snippets and pointers for things I need to do fairly often, but not often enough that I can remember.

- [Data Cleaning:](./Cheatsheet_Rdatacleaning.html) A list of commands for doing data cleaning/wrangling tasks.
 
- [Plotting:](./Cheatsheet_Rplotting.html) A list of commands for plotting in R (both base plot and ggplot).

- [Text Manipulation:](./Cheatsheet_Textmanipulation.html) A list of commands for working with text.



## Acknowledgements

This site is maintained by [Andreas Handel](https://www.andreashandel.com/).

```{r, results = "asis", echo = FALSE, message = FALSE, warning=FALSE}
#the following code snipped is taken from Hadley's R4DS intro page
library(dplyr)
contributors <- readr::read_csv("contributors.csv", col_types = list())
contributors <- contributors %>% 
  mutate(
    link = glue::glue("[\\@{GithubID}](https://github.com/{GithubID})"),
    desc = ifelse(is.na(LastName), link, glue::glue("{FirstName} {LastName} ({link})"))
  )
cat("The following individuals have contributed to improving the course:\n")
cat(paste0(contributors$desc, collapse = ", "))
```

The site is licensed under the [Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License](http://creativecommons.org/licenses/by-nc-sa/4.0/). Linked materials are governed by their own licenses. 